Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2017-03-05 manuscript/editor_response2_tree_physiology.Rmd
final edits to response#2

\
*Response*: Although both studies with rubber trees are extremely interesting in terms of the dymanics of storage carbohyrdate accumluation and mobilization, they lack empirical data for photosynthesis rates and only speculate about the impacts on growth. I have choosen to not mention them in the introduction, as they are mostly out of context with discusssion of the effects of sink limitation on physiological processes and growth.

@@

\
*Response*: We have corrected to this statement to include observed values of *g*~s~, *A*~sat (which includes C~a~ of 400) and vapor presssure deficit.

@@

\
*Response*: Reference to Atkin has been removed.

@@

\
*Response*: We have now introducted the term *A*~mass~ in this section as it had not been previously described.

@@

\
*Response*: We have reworded the desciprtion of the findings with the g~1~ parameter. "The *g*~1~ parameter ... was highest in the smaller containers and decreased in larger containers and the Free seedling treatment"

>>>>

\
*Response*: Although both studies with rubber trees are extremely interesting in terms of the dynamics of storage carbohydrate accumulation and mobilization, they lack empirical data for photosynthesis rates and only speculate about the impacts on growth. We have chosen to not mention them in the introduction, as they are mostly out of context with discussion of the effects of sink limitation on photosynthesis and growth.

@@

\
*Response*: We have corrected to this statement to include observed values of *g*~s~, *A*~sat~ (which includes C~a~ of 400) and vapor pressure deficit.

@@

\
*Response*: Reference to Atkins has been removed.

@@

\
*Response*: We have now introduced the term *A*~mass~ in this section as it had not been previously described.

@@

\
*Response*: We have reworded the description of the findings with the g~1~ parameter. "The *g*~1~ parameter ... was highest in the smaller containers and decreased in larger containers and the Free seedling treatment"
